Reliable Inferences from Simply Parameterised Models

### 2012-08-29 ms.tex
Results from fit

A commonly suggested technique \citep[e.g.][]{gregory} to avoid this situation
is to add an ``error-bar boost'' parameter which we will call $\kappa$.
This adds one more parameter to the list, and the likelihood becomes:
\begin{eqnarray}
p(\yy|A, c, w, \kappa) &=& \prod_{i=1}^N
\frac{1}{(\kappa\sigma)\sqrt{2\pi}}
\exp
\left[
-\frac{1}{2(\kappa\sigma)^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
\right] \\
&\propto& \kappa^{-N}\exp\left[-\frac{1}{2(\kappa\sigma)^2}\sum_{i=1}^N\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2\right]
\end{eqnarray}

>>>>

A commonly suggested technique \citep[e.g.][]{gregory} to avoid this situation
is to add an ``error-bar boost'' parameter which we will call $\kappa$.
This adds one more parameter to the list, and the likelihood becomes:
\begin{eqnarray}
p(\yy|A, c, w, \kappa) &=& \prod_{i=1}^N
\frac{1}{(\kappa\sigma)\sqrt{2\pi}}
\exp
\left[
-\frac{1}{2(\kappa\sigma)^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
\right] \\
&\propto& \kappa^{-N}\exp\left[-\frac{1}{2(\kappa\sigma)^2}\sum_{i=1}^N\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2\right]
\end{eqnarray}
We ran this model through DNest and found that it also does not work. The
true value of $F$ is 1, and the inferred values of $F$ are
$(0.9401 \pm 0.0072)$ and $(0.9404 \pm 0.0083)$
respectively. The true value is an $8.3-\sigma$ outlier from the posterior
using the simple model, and this is only reduced to $7.2-\sigma$ by the
inclusion of the ``sigma-boost'' parameter $\kappa$. Clearly this is an
unsatisfactory situation.
